---
title: "Data Tables"
author: "rswaty"
date: "2020-08-31"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction
This page includes some raw data tables for exploration.


## Load libraries

```{r message=FALSE, warning=FALSE}
library(readr)
library(DT)
```

## Load data

```{r message=FALSE, warning=FALSE}
vdepParcelAcres <- read_csv("data/vdepParcelAcres.csv")

raw <- read_csv("data/raw.csv")

acresBpS <- read_csv("data/acresBpS.csv")
```

## Three data tables
Just to illustrate possibilities and the structure of the data we load in three datatables.  You can search and sort.

### Acres per BpS, inside/outside of protected status

```{r}
datatable(acresBpS, class = 'cell-border stripe')
```

<br>

###  Vegetation Departure by Parcel over the 3 LANDFIRE versions

```{r}
datatable(vdepParcelAcres, class = 'cell-border stripe')
```


### Raw data
This is the data as processed by Sarah Hagen
```{r}
datatable(raw, class = 'cell-border stripe')
```





