---
title: "VDEP for LANDFIRE Grouped Vegetation Types for 2008, 2010 and 2012"
author: "rswaty"
date: "2020-08-28"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction
For fun exploring VDEP for  Grouped Vegetation Types within the file Sarah Hagen sent.  Data table made in Excel Pivot table.  Pivot table work required some specific actions:
*  Used "Label_version" (e.g. LABEL_105) as a filter to remove "non-natural" vegatation types (e.g. Burnable Ag) and "Open Water"
*  Averages calculated in Excel
*  Removed some Grouped Vegatation types such as Agriculture and Barren.

Father-in-law used to day "Now Randy, don't accomplish something that doesn't accomplish anything", which I may have done here.


### Install libraries

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
library(readr)
library(ggplot2)
library(tidyverse)
```

### Load and explore data

```{r}

groupVegVDEP <- read_csv("data/groupVegVDEP.csv")


head(groupVegVDEP)
tail(groupVegVDEP)
str(groupVegVDEP)
```



### Make a chart

```{r}

groupVegVDEPchart <- groupVegVDEP %>%
  ggplot(aes(x= Version, y = VDEP)) +
  facet_wrap(~GroupVeg, scales = "free_x") +
    scale_x_continuous(breaks = groupVegVDEP$Version, labels=groupVegVDEP$Version) +
    geom_bar(stat = "identity") +
    labs(x = "Version",
         y = "VDEP",
          title = "Vegetation Departure (VDEP) for LANDFIRE Grouped Vegetation Types",
          subtitle = "Averaged across all parcels; lower VDEP = closer to reference conditions",
          caption = "From NEY_im_f_BpS_VDEP dataset by Sarah Hagen") +
    theme(plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", 
        plot.caption.position =  "plot") +
      theme_bw()

groupVegVDEPchart
```


### Notes
There are some Grouped Vegetation Types that show changed VDEP over time.  The changes may be at least partially driven by improvements in methodology.  





