---
title: "malBpS"
author: "rswaty"
date: "2020-09-14"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Biophysical Settings for the MAL region (not "mal" as in "bad" as in Spanish)

Exploring some basic questions about "representation" of Biophysical Settings (historic vegetation types) within and outside of TNC ownership, by region.

GIS processing by Sarah Hagen.

### Libraries

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
library(ggpubr)
```



### Read in and wrangle datasets

Need tidy data with these columns:

* BPS_MODEL
* In/Out (treatment essentially)
* Acres
* Percent of total 

```{r}
# read in data, removing unwanted colunms
malConusBpS <- read_csv("data/malConusBpS.csv", 
    col_types = cols(BPS_CODE = col_skip(), 
                     BPS_MODEL = col_skip(), 
                     ZONE = col_skip(), 
                     GROUPID = col_skip(), 
                     GROUPMODEL = col_skip(), 
                     GROUPNAME = col_skip()))

malNatureBpS <- read_csv("data/malNatureBpS.csv", 
        col_types = cols(BPS_CODE = col_skip(), 
                     BPS_MODEL = col_skip(), 
                     ZONE = col_skip(), 
                     GROUPID = col_skip(), 
                     GROUPMODEL = col_skip(), 
                     GROUPNAME = col_skip()))

head(malConusBpS)
head(malNatureBpS)

# group and summarize by COUNT
malConusBpS <- malConusBpS %>%
  group_by(BPS_NAME, 
           GROUPVEG,
           InOrConus) %>%
  summarise(sum(COUNT)) 
# rename new column
names(malConusBpS)[names(malConusBpS) == "sum(COUNT)"] <- "COUNT"

malNatureBpS <- malNatureBpS %>%
  group_by(BPS_NAME, 
           GROUPVEG,
           InOrConus) %>%
  summarise(sum(COUNT))

# rename new column
names(malNatureBpS)[names(malNatureBpS) == "sum(COUNT)"] <- "COUNT"

# add in acres and percent
malConusBpS <- malConusBpS %>%
  mutate(acres = (COUNT*0.222)) %>%
  mutate(percent = (COUNT/(sum(COUNT)*100)))

malNatureBpS <- malNatureBpS %>%
  mutate(acres = (COUNT*0.222)) %>%
  mutate(percent = (COUNT/(sum(COUNT)*100)))

# add tables-make long
malBpS <- rbind(malConusBpS, malNatureBpS)

#merge to compare side by side

mergedMalBpS <- merge(malConusBpS, malNatureBpS, by = "BPS_NAME") %>%
  mutate(difference = percent.x - percent.y) %>%
  mutate(percentTotal = (acres.y/acres.x)*100)




```



### Percent of Total ("representation")

```{r, fig.width=12, fig.height=8}

malRep <-
ggdotchart(mergedMalBpS, x = "BPS_NAME", y = "percentTotal",
           color = "GROUPVEG.x",                                # Color by groups
           palette = c("#00AFBB", "#E7B800", "#FC4E07", "#7d0b0b", "#7d0b0b", "#2b2424" ), # Custom color palette
           sorting = "descending",                       # Sort value in descending order
           add = "segments",                             # Add segments from y = 0 to dots
           rotate = TRUE,                                # Rotate vertically
           group = "GROUPVEG.x",                                # Order by groups
           dot.size = 6,                                 # Large dot size
           ggtheme = theme_pubr()                        # ggplot2 theme
           )

malRep
```


















