---
title: "Acres per parcel"
author: "Randy Swaty"
date: "2020-08-28"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction

Here I will explore with this workflowR package and will simply chart out parcel size.  

### Install libraries

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
library(readr)
library(ggplot2)
library(tidyverse)
library(scales)
```

### Load and explore data

```{r}

parcelAcres <- read_csv("data/parcelAcres.csv")


head(parcelAcres)
tail(parcelAcres)
str(parcelAcres)
```

### A Chart to explore parcel size

```{r parcelChart, echo=TRUE, message=FALSE, warning=F}
parcelSizeChart <- parcelAcres %>%
  ggplot(aes(x= newID, y = ACRES)) +
  scale_y_continuous(labels = comma) + 
    geom_point(fill="#69b3a2", color="firebrick", alpha=0.8) +
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank())+
    labs(x = "One dot per parcel",
         y = "Acres",
          title = "Parcel size",
          subtitle = "Most are too small for subsequent analysis",
          caption = "From NEY_im_f_BpS_VDEP dataset by Sarah Hagen") +
    theme(plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", 
        plot.caption.position =  "plot") +
      theme_bw()

parcelSizeChart

```


### What to do now?
Most of the parcels, actually ~99% of them are really small, too small for VDEP calculations.  We still need to do *something* to help quantify **condition**, and explore effectiveness of strategies.  Ideas include:

* Look to "project" area instead of "parcel" area
* Consider VDEP or other metrics for large parcels only
* Look at ways to combine data and use rulesets for smaller data
* Find other datasets that are more appropriate for use at smaller extents

