---
title: "Vegetation Departure for Parcels"
author: "rswaty"
date: "2020-08-31"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction
The main questions of this work are "does vegetation condition change over time?' and "is there a difference in vegetation condition inside and outside of TNC* protected areas?"

Here we explore Vegetation Departure (VDEP) by version, inside and outside of TNC protected (fee and easement, *may not be currently owned by TNC*). 



## Load libraries

```{r message=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
library(yarrr)
```

## Read in and pivot data


```{r}
# load data
yesNoVdep <- read_csv("data/yesNoVdep.csv")

head(yesNoVdep)

#  pivot long
vdepLong <- yesNoVdep %>%
  pivot_longer(!Protected, names_to = "Version", values_to = "VDEP")

head(vdepLong)
```

## Make a Pirate Plot
This type of plot shows (https://bookdown.org/ndphillips/YaRrr/pirateplot.html):
* VDEP of each parcel (dots)
* Mean (central horizontal bar)
* Density ("bean" or colored polygon)
* Standard Deviation (box)

```{r}

yarrr::pirateplot(formula = VDEP ~ Protected + Version, 
                  data = vdepLong,           
                  main = "Vegetation Depature over 3 versions",
                  theme = 0,
                  inf.method = 'sd',
                  pal = "southpark", # southpark color palette
                  bean.f.o = .6, # Bean fill
                  point.o = .3, # Points
                  inf.f.o = .3, # Inference fill
                  inf.b.o = .8, # Inference border
                  avg.line.o = 0.7, # Average line
                  bar.f.o = .3, # Bar
                  inf.f.col = "white", # Inf fill col
                  inf.b.col = "black", # Inf border col
                  avg.line.col = "black", # avg line col
                  bar.f.col = gray(.8), # bar filling color
                  point.pch = 21,
                  point.bg = "white",
                  point.col = "black",
                  point.cex = .7)

```

## Quick Take Home Messages

* VDEP does not vary over time, or between protection level.  
* Any variation could be due to methods, or actual change in vegetation conditions
* Recommend different approach
